Empty Homes V1

### 2017-06-06 EmptyHomesV1.Rmd
Bootsrapped results
Worked through the bootstrapping process unpicking errors that had been made on the first attempt.

prices %>% filter(X14== "GREATER LONDON") %>% summarise(mean = mean(X2))
Admin_ward_code
#c("Lower Mainstream", "Mid Mainstream", "Upper Mainstream", "Prime", "Super Prime"),
test <- prices %>% 
  filter( Admin_district_code =="E09000020") %>%
  mutate(class = cut(X2, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
            labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
             right = F)) %>%
  select(Admin_ward_code, class) %>%
  group_by(Admin_ward_code, class) %>% 
  summarise(Counts = n()) %>%
  group_by(Admin_ward_code) %>%
  mutate(WardPerc = Counts/sum(Counts)) %>%
  ungroup

test3 <- Chelseainfo %>% 
  group_by(Admin_ward_code) %>%
  summarise_all(funs(first)) %>%
  select(Admin_ward_code, WardLowUse, WardHomes) %>%
  left_join(., test, "Admin_ward_code") %>%
  mutate(LowUseClass = WardLowUse*WardPerc,
         HomesClass = WardHomes*WardPerc) %>%
  group_by(class) %>%
  summarise(LowUseClass = sum(LowUseClass),
            HomesClass = sum(HomesClass)) %>%
  filter(complete.cases(.)) %>%
  mutate(PercOfLowUse = LowUseClass/sum(LowUseClass),
         PercOfHomes = HomesClass/sum(HomesClass),
         PercofClass = LowUseClass/HomesClass,
         `Expected Homes` = PercOfHomes*sum(LowUseClass),
         `Actual Homes` = PercOfLowUse*sum(LowUseClass))

@@

```{r}
 ChelPrice <- prices %>% 
  filter( Admin_district_code =="E09000020") %>%
  select(lsoa11cd, Price =X2) %>%
  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
            labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
             right = F))

@@

@@

test <- unique(ChelPrice$lsoa11cd)%>% 
  map(~ ChelPrice %>% 
        filter(lsoa11cd == .x) %>% 
  ClassStrapper(., sum((filter(Chelseainfo, LSOA_CODE == .x))$LowUse)) %>%
    mutate(class = as.character(class),
           Counts = as.integer(Counts),
           ID = as.integer(ID)) %>%
      setNames(c("class", paste0("Counts", .x) ,"ID"))
  )

ChelseaLSOAstrap <- test %>%  
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE)) %>%
select(class, ID, Totals)

@@

@@

>>>>

prices %>% filter(X14== "GREATER LONDON") %>% summarise(mean = mean(X2))
Admin_ward_code
#c("Lower Mainstream", "Mid Mainstream", "Upper Mainstream", "Prime", "Super Prime"),
ClassCountsPerWard <- prices %>% 
  filter( Admin_district_code =="E09000020") %>%
  mutate(class = cut(X2, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
            labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
             right = F)) %>%
  select(Admin_ward_code, class) %>%
  group_by(Admin_ward_code, class) %>% 
  summarise(Counts = n()) %>%
  group_by(Admin_ward_code) %>%
  mutate(WardPerc = Counts/sum(Counts)) %>%
  ungroup

test3 <- Chelseainfo %>% 
  group_by(Admin_ward_code) %>%
  summarise_all(funs(first)) %>%
  select(Admin_ward_code, WardLowUse, WardHomes) %>%
  left_join(., ClassCountsPerWard, "Admin_ward_code") %>%
  mutate(LowUseClass = WardLowUse*WardPerc,
         HomesClass = WardHomes*WardPerc) %>%
  group_by(class) %>%
  summarise(LowUseClass = sum(LowUseClass),
            HomesClass = sum(HomesClass)) %>%
  filter(complete.cases(.)) %>%
  mutate(PercOfLowUse = LowUseClass/sum(LowUseClass),
         PercOfHomes = HomesClass/sum(HomesClass),
         PercofClass = LowUseClass/HomesClass,
         `Expected Homes` = PercOfHomes*sum(LowUseClass),
         `Actual Homes` = LowUseClass)

@@

```{r}
 ChelPrice <- prices %>% 
  filter( Admin_district_code =="E09000020") %>%
  select(Admin_ward_code, lsoa11cd, Price =X2) %>%
  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
            labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
             right = F))

round(table(ChelPrice$class)/nrow(ChelPrice)*100)

@@

Chelseastrapped %>% group_by(class)%>%
  summarise(Counts = mean(Counts)) %>%
  mutate(ratio = Counts/sum(Counts))

@@

ChelseainfoWard <- Chelseainfo %>%
  group_by(Admin_ward_code) %>%
  summarise_all(funs(first))

set.seed(16540)
ChelseaLSOAstrap1 <- unique(ChelPrice$Admin_ward_code)%>% 
  map(~ ChelPrice %>% 
        filter(Admin_ward_code == .x) %>% 
  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardLowUse)) %>%
    mutate(class = as.character(class),
           Counts = as.integer(Counts),
           ID = as.integer(ID)) %>%
      setNames(c("class", paste0("Counts", .x) ,"ID"))
  )

ChelseaLSOAstrap <- ChelseaLSOAstrap1 %>%  
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE),
         class = fct_relevel(class, "Upper", after = 2)) %>%
select(class, ID, Totals)

#bootrapps Chelsea housing stock.
set.seed(16540)
ChelseaWardHomesStrap1 <- unique(ChelPrice$Admin_ward_code)%>% 
  map(~ ChelPrice %>% 
        filter(Admin_ward_code == .x) %>% 
  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardHomes)) %>%
    mutate(class = as.character(class),
           Counts = as.integer(Counts),
           ID = as.integer(ID)) %>%
      setNames(c("class", paste0("Counts", .x) ,"ID"))
  ) %>%  
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE),
         class = fct_relevel(class, "Upper", after = 2)) %>%
select(class, ID, Totals)

@@

test1 <- ChelseaWardHomesStrap1  %>% left_join(., ChelseaLSOAstrap, by = c("class", "ID")) %>%
  rename(LowUse = Totals.y,
         Homes = Totals.x) %>%
  group_by(ID)%>%
  mutate(ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes),
         LowUsePerc = LowUse/sum(LowUse),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse),
         RatioExvsAct = LowUse/ExpectedHomes)

@@

test1 %>% ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Boxplot of bootstrapped Ratios")

test1 %>% group_by(class) %>%
  summarise(meanC = mean(Counts), 
            meanT = mean(Totals), 
            meanR = mean(ratio))

ChelseaWardHomesStrap1 %>% group_by(class) %>%
  summarise(meanC = mean(Totals))
